\documentclass{resume}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage[tmargin=0.6in,rmargin=0.75in,lmargin=0.75in,bmargin=0.6in]{geometry}%
%
\name{Matthew Lopez}%
\address{(909){-}141{-}547 | mlopez@calpoly.edu}%
%
\begin{document}%
\pagestyle{empty}%
\normalsize%
\begin{flushleft}%
\newcommand{\EducationEntry}[1]{
                            {\bf California Polytechnic State University}
                            \hfill
                            {\em September {#1} - Present}
                        }%
\newcommand{\BoldHeading}[1]{
                            {\bf{#1}}
                        }%
\newcommand{\DatedEntry}[2]{
                            \item{#1} 
                            \hfill
                            {\em{#2}}
                        }%
\newcommand{\FirstDatedEntry}[2]{
                            \text{#1} 
                            \hfill
                            {\em{#2}}
                        }%
\begin{rSection}{Education}%
\EducationEntry{2019}%
\linebreak%
Bachelor of Science in Software Engineering%
\linebreak%
Projected graduation date: June 2023%
\end{rSection}%
\begin{rSection}{Work Experience}%
\begin{rSubsection}{Amazon {-} Los Angleles}{\textit{June 2018}}{Web Developer}{}%
\item{Worked with realistic 3D modeling. Learned about implementing advanced physics engines}%
\begin{rSubsection}{Adobe {-} Los Angleles}{\textit{May 2019}}{Systems Software Developer}{}%
\item{Worked with realistic 3D modeling. Learned about implementing advanced physics engines}%
\begin{rSubsection}{Cisco {-} Santa Barbara}{\textit{June 2018 {-} August 2018}}{Web Developer}{}%
\item{Worked with realistic 3D modeling. Learned about implementing advanced physics engines}%
\end{rSubsection}%
\end{rSection}%
\begin{rSection}{Projects}%
\BoldHeading{Pixel art generator}%
\linebreak%
Built a tool that takes an image as input and samples the image to produce pixel art as output. Learned about CSS and Pylatex. %
\linebreak%
\linebreak%
\BoldHeading{Procedurally Generated Map Maker}%
\linebreak%
Browser{-}based application that allows users to procedurally generate a terrain map based on a random seed.%
\linebreak%
\linebreak%
\BoldHeading{Pixel art generator}%
\linebreak%
Built a tool that takes an image as input and samples the image to produce pixel art as output. Learned about CSS and Pylatex. %
\end{rSection}%
\begin{rSection}{Relevant Coursework}%
\text{CPE 101 Fundamentals of Computer Science}%
\item{CPE 202 {-} Data Structures}%
\item{CPE 123 {-} Introduction to Computing}%
\end{rSection}%
\begin{rSection}{Soft Skills}%
Goal setting, Friendliness, Analysis, Influence%
\end{rSection}%
\end{flushleft}%
\end{document}